\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2021-02-08 analysis/paper/casebase-manuscript.Rmd
remove coxRidge

Several packages implement penalized estimation for the Cox model: \pkg{glmnet} [-@regpathcox], \pkg{glmpath} [-@park_hastie], \pkg{penalized} [-@l1penal], \pkg{riskRegression} [-@gerds_blanche]. Moreover, some packages also include penalized estimation in the context of Cox models with time-varying coefficients: elastic-net penalization with \pkg{CoxRidge} [-@perperoglou] and \pkg{rstpm2} [-@clements_liu], while \pkg{survival} [-@survival-package] has an implementation of ridge-penalized estimation. On the other hand, our package \pkg{casebase} provides penalized estimation of the hazard function. To our knowledge, \pkg{casebase} and \pkg{rsptm2} are the only packages to offer this functionality.

@@

\textbf{CoxRidge}        &                          & \checkmark                         & \checkmark                     &                  &                     & \checkmark                        &                                  &                                  \\ \hline

>>>>

Several packages implement penalized estimation for the Cox model: \pkg{glmnet} [-@regpathcox], \pkg{glmpath} [-@park_hastie], \pkg{penalized} [-@l1penal], \pkg{riskRegression} [-@gerds_blanche]. Moreover, some packages also include penalized estimation in the context of Cox models with time-varying coefficients: elastic-net penalization with \pkg{rstpm2} [-@clements_liu], while \pkg{survival} [-@survival-package] has an implementation of ridge-penalized estimation. On the other hand, our package \pkg{casebase} provides penalized estimation of the hazard function. To our knowledge, \pkg{casebase} and \pkg{rsptm2} are the only packages to offer this functionality.

@@
